DeepSched: A Deep Representation Of Scheduling Policies For Heterogeneous Distributed Systems

### 2020-04-12 paper/core/conclusion.tex
added future work

@@

>>>>

\subsection{Conclusion}

@@

\subsection{Future Work}

This work can be improved in two possible ways. \emph{First,} other heterogeneous task scheduling methods can be approximated using neural networks. As we mentioned, the proposed method can be expanded to approximate other scheduling methods as long as static scenarios provided. Neural networks can even approximate theoretical methods, that achieves optimal results, to a great extend. These methods aren't used in real life due to there time complexity. However, if these methods are approximated using neural networks, they can be deployed in real life applications.

\emph{Second,} Other possible approximation methods can be tried through neural networks in order to confront dynamic scenarios. Online optimization can be one solution, however online network optimization can be very computationally-expensive. Another possible solution is to use the proposed network as a function approximator in a \emph{Reinforcement Learning} (RL) environment, in order to be able to learn dynamically in case of new introduced tasks.

### 2020-04-12 paper/core/results.tex
added abstract
added future work

@@

\subsection{Results Discussion}
The previous results show that neural networks can approximate a scheduling algorithm for heterogeneous distributed systems, resulting in a significantly-good performance and fast execution. The proposed network can perform well, even on unseen data it can produce efficient schedules.

>>>>

\begin{figure}[hp]
    \centering
    \includegraphics[width=0.45\textwidth]{diagrams/ta_chart}
    \caption{Average turnaround time produced from the three discussed schedulers at different input sizes.}
    \label{fig:ta_chart}
\end{figure}

@@

\subsection{Results Discussion}
The previous results show that neural networks can approximate a scheduling algorithm for heterogeneous distributed systems, resulting in a significantly good performance and fast execution. The proposed network can perform well, even on unseen data it can produce efficient schedules.
